Affect of COVID-19 on the lives of Toronontians

### 2022-02-07 outputs/paper/paper.Rmd
FINAL COMMIT

From a statistical point of view, there can be some confusion with the "source of infection" observation because there is a lot of overlap between the source being "close contact" and "household contact" due to the fact that an individual can fall under both. This lack of clear distinction between categories can introduce bias into the dataset because our data does not accurately display what should be displayed. Another category that I felt could have been holding this dataset back from providing even more accurate data was the age category, specifically the option where the individual was ages "19 or younger." The problem with grouping the age in a category like this is that it includes toddlers, children and young adults and all of these groups of people are likely to have different behaviors. This means that if a lot of children catch the virus from school or household contact, it automatically groups younger adults into that conclusion as well even if they are not to blame. This can cause problems with decisions that governments may have to make, for example, closure of schools, a place you would find children, and high schools, a place with younger adults. I

@@

There could be a possible case of self-serving bias where an individual downplays qualities that they feel are less desirable [@citebias]. From figure 5 this sort of bias seems more clear because it suggests that of all sources of infection for the virus, the most common source is "no information." The high proportionality of younger respondents seem who were not able to provide any information about their reported/probable case of COVID-19 could be an example of self-serving bias in this dataset as individuals may not prefer saying the truth about how the virus was contracted as it could put them in a position where it looks like government regulations were not followed. This is also a weakness in this dataset as well since it isn't able to give any information about how the virus was contracted. This type of information is important for the government and even someone looking at the dataset because it helps them be informed of the most probable source of the infection.

>>>>

From a statistical point of view, there can be some confusion with the "source of infection" observation because there is a lot of overlap between the source being "close contact" and "household contact" due to the fact that an individual can fall under both. This lack of clear distinction between categories can introduce bias into the dataset because our data does not accurately display what should be displayed. Another category that I felt could have been holding this dataset back from providing even more accurate data was the age category, specifically the option where the individual were ages "19 or younger." The problem with grouping the age in a category like this is that it includes toddlers, children and young adults and all of these groups of people are likely to have different behaviors. This means that if a lot of children catch the virus from school or household contact, it automatically groups younger adults into that conclusion as well even if they are not to blame. This can cause problems with decisions that governments may have to make, for example, closure of schools, a place you would find children, and high schools, a place with younger adults.

@@

There could be a possible case of self-serving bias where an individual downplays qualities that they feel are less desirable [@citebias]. From figure 5 this sort of bias seems more clear because it suggests that of all sources of infection for the virus, the most common source is "no information." The high proportionality of younger respondents seem who were not able to provide any information about their reported/probable case of COVID-19 could be an example of self-serving bias in this dataset as individuals may not prefer saying the truth about how the virus was contracted as it could put them in a position where it looks like government regulations were not followed. This is also a weakness in this dataset since it isn't able to give any information about how the virus was contracted. This type of information is important for the government and even someone looking at the dataset because it helps them be informed of the most probable source of the infection.
